The Concurrent Calculi Formalisation Benchmark

### 2024-02-23 short-paper/short-paper.tex
Remove a todo that I think is done.

Ultimately, the fundamental aspects covered by our benchmark serve as the building blocks for most current research on concurrent calculi.
It is our hope and aim that exploring solutions to our challenges will move the community closer to a future where the key basic proof techniques for concurrent calculi are as easy to mechanise as they are to write on paper.

\todo{A sentence to conclude reiterating the relevance of the challenges}
\bibliographystyle{splncs04}
\bibliography{../references}

>>>>

Ultimately, the fundamental aspects covered by our benchmark serve as the building blocks for most current research on concurrent calculi.
It is our hope and aim that exploring and comparing solutions to our challenges will move the community closer to a future where the key basic proof techniques for concurrent calculi are as easy to mechanise as they are to write on paper.

\bibliographystyle{splncs04}
\bibliography{../references}
